\paragraph*{}In this paper $A$ is the set of all arms and $|A|=K$ denotes the number of arms in the set. Any arm i is denoted by $a_{i}$ and the optimal arm is denoted by $a^{*}$. The '*' superscript is used to denote anything related to optimal arm. In all the proofs it is assumed that there is only one optimal arm. The average estimated payoff for any arm is denoted by $\hat{r}_{i}$ whereas the true mean of the distribution from which the rewards are sampled is denoted by $r_{i}$ and $r_{i}\in[0,1]$. $\Delta_{i}=r^{*}-r_{i}$ and $\hat{\Delta}_{i}=\hat{r}^{*}-\hat{r}_{i}$.So, $\Delta_{i}\in [0,1], \forall i\in A$ In most of the events $\xi$ it is taken that $\hat{r}_{s}$ is $\max{a_{i}},\forall i \in A$, $\hat{r}_{m}$ is $\min{a_{i}},\forall i \in A$ and $\hat{\Delta}_{s}=\hat{r}_{s} - \hat{r}_{m}$ which gives the total range within which $\hat{r}_{i},\forall i\in A$ lies. In all cases $\min_{i\in A}{\Delta_{i}}$ is denoted by $\Delta$. $c_{i}$ in most proofs denotes the confidence interval for arm $a_{i}$. $\psi(|A|)$ in this work is defined as a monotonically decreasing function over $|A|$ which decreases after every round.
\paragraph*{}It is assumed that the distribution from which rewards are sampled are identical and independent sub-Gaussian distributions. Throughout the paper, we assume that the distributions $v_{i}$ are sub-Gaussian that is $\int e^{\lambda(x - r)} v_{i} (dx) ≤ e^{\lambda /2}, \forall \lambda \in \mathbb{R}$. Note that these include Gaussian distributions with variance less than 1 and distributions supported on an interval of length less than 2. All the experiments are also conducted with sub-Gaussians having variance as 1. Together with a Chernoff-Hoeffding bound, the sub-Gaussian assumption implies the following concentration inequality, valid for any
$u > 0$,
\newline
\hspace*{8em}$\mathbb{P}\lbrace \hat{r}_{i} - r^{*} > u\rbrace \leq exp(-\dfrac{su^{2}}{2}) $
\newline
where s is the number of pulls of $a_{i}$. T is the horizon over which this entire algorithm runs.  $A^{'}$ at any round $m$ denotes the arms still not eliminated.
%\paragraph*{}The paper is organized as follows. We first present the algorithm in section 6. We then provide the proofs of Phase1 which includes regret-bound calculation and arm deletion conditions in section 7. In section 8, we provide proofs for Phase2 along with early stopping conditions. Section 9 deals with regret bound and then we provide error probability and error bounds in section 10. Experimental results are provided in section 11, and we conclude in section 12.